## Evolutionary History of the Main Biological Characters of Siphonophores

### 2017-02-13 character_coding/CharacterEvolution.Rmd
separated make.simmaps from plotSimmaps

@@

>>>>

```{r, echo=F}
#Make simmap objects
make.simmap(ultratree, sex, nsim = 100) -> sex_sim
make.simmap(ultratree, palpons, nsim = 100) -> palpons_sim
make.simmap(ultratree, tentilla, nsim = 100) -> tentilla_sim
make.simmap(ultratree, nectosome, nsim = 100) -> nectosome_sim
make.simmap(ultratree, necto_pos, nsim = 100) -> necto_pos_sim
make.simmap(ultratree, necto_types, nsim = 100) -> necto_types_sim
make.simmap(ultratree, pneuma, nsim = 100, pts=T) -> pneuma_sim
make.simmap(ultratree, bracts, nsim = 100) -> bracts_sim
make.simmap(ultratree, vrange, nsim = 100) -> vrange_sim

@@

###Presence of palpons:
```{r, echo=F}
#Simmap PALPONS
plotTree(ultratree, lwd = 4)
palpons_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(palpons_sim)
```

###Presence of tentilla:
```{r, echo=F}
#Simmap TENTILLA
plotTree(ultratree, lwd = 4)
tentilla_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim)
```

###Presence of Nectophores:
```{r, echo=F}
#Simmap NECTOSOME
plotTree(ultratree, lwd = 4)
nectosome_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(nectosome_sim)
```

###Position of Nectosome:
```{r, echo=F}
#SIMMAP NECTOSOME POSITION
plotTree(ultratree, lwd = 4)
necto_pos_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red", "green")
names(colors) = c("Dorsal", "No nectosome", "Ventral")
nodelabels(pie=(describe.simmap(necto_pos_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

###Nectophore number and types:
```{r, echo=F}
#Simmap NECTOPHORE TYPES
plotTree(ultratree, lwd = 4)
necto_types_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red", "green", "blue")
names(colors) = c("Multiple of one type", "None", "Two of one type", "Two of two types")
nodelabels(pie=(describe.simmap(necto_types_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

###Presence of Pneumatophore:
```{r, echo=F}
#Simmap PNEUMATOPHORE
plotTree(ultratree, lwd = 4)
pneuma_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(pneuma_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(pneuma_sim)
```

###Number of Bract types:
```{r}
#Simmap bract-types
plotTree(ultratree, lwd = 4)
bracts_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red", "green3", "blue")
names(colors) = c("No bracts", "1", "2", "4")
nodelabels(pie=(describe.simmap(bracts_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

###Ocean Depth Zones:
```{r, echo=F}
#Simmap Vertical.Range
plotTree(ultratree, lwd = 4)
vrange_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "cyan", "blue", "green", "red")
names(colors) = c("Bathypelagic", "Surface", "Mesopelagic", "Epipelagic", "Deep benthic")
nodelabels(pie=(describe.simmap(vrange_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```
